---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GeoMSNA2022

<!-- badges: start -->
<!-- badges: end -->

The goal of GeoMSNA2022 is to facilitate geospatial and remote sensing analyses of selected global `MSNA`s.

Prior to the creation of this repository various RS variables have been extracted for 6 MSNA data sets (SOM, IRQ, COL, NER, NGA, and HTI). The extraction process is currently performed and documented in the `surveyGEER` package repository. Now that the variables have been extracted we aim to explore relationships between environmental/climatic/geospatial phenomena and household conditions. 

It is recommended the country-offices with R-capacity use this repository to host this stage of analysis. 


## Recommendations

- We recommend starting with Exploratory Data Analysis (EDA) using rmarkdown notebooks. You can simply run `usethis::use_vignettes()` to automatically create a markdown notebook
- Once exploratory data analysis has been performed the analyst should be sure to use weights for final analysis


## First Steps

You will need to decide on the variables in the HH data set that should be analyzed though a geospatial/climatic/environmental lens. Once you have done this you will find  a rudimentary function called `load_core_hh_indicators.R` in the `R/` directory of this project. You can then add them to the function following the lead the `irq` team has provided. If you have the same variables as another country make sure you copy there label to use in your list.

```{r, eval =F}

load_core_hh_indicators <-  function(input_df, country_code="irq"){
  if (country_code=="irq"){
    res <- list(
      # labels on left - column names on right
      `Food Consumption Score (numeric)`= "fcs",
      `Food Consumption Score (categorical)`= "fcs_category",
      `Household Hunger Scale (categorical)` = "household_hunger_scale",
      `main source of food (categorical)` = "food_source",
      `HHH unemployed (categorical)` = "unemployed_seek_work",
      `HH debt (numeric)` = "how_much_debt",
      `debt per member > 90k (categorical)` = "g37"
      
    )
    
  }
  if(country_code=="som"){
    res <- list(
      `Respondent Gender` = "respondent_gender",
      `Respondent Age` = "respondent_age",
      `Region` = "region",
      `District` = "district",
      `Reside in an IDP settlement` = "idp_settlement",
      `Village/settlement/IDP site` = "settlements",
      `Household Size` = "hh_size",
      `Household's total cash income from all income sources` = "total_house_income",
      `If yes, what is yoour household's current total amount of debt in USD` = "total_hh_debt",
      `Drinking` = "drinking_water",
      `Cooking` = "cooking_water",
      `Personal hygiene (washing or bathing)` = "hygiene_water",
      `Other domestic purposes (cleaning house, floor, etc.)` = "domestice_water",
      `FSL shocks Unusually high food prices` = "hh_fsl_shocks/high_food_prices",
      `FSL shocks Drought/irregular rains, prolonged dry spell` = "hh_fsl_shocks/drought",
      `FSL shocks Unusually high level of crop pests and disease` = "hh_fsl_shocks/crop_disease",
      `FSL shocks Disease outbreak in the settlement` = "hh_fsl_shocks/disease_outbreak",
      `FSL shocks Too much rain, flooding` = "hh_fsl_shocks/flooding",
      `FSL shocks Livestock disease outbreak` = "hh_fsl_shocks/livestock_disease",
      `No food to eat of any kind in your house because of lack of resources to get food` = "hh_no_food",
      `How often did this happen in the past [4 weeks/30 days]` = "hh_no_food_freq",
      `Go to sleep at night hungry because there was not enough food` = "hh_hunger",
      `How often did this happen in the past [4 weeks/30 days]` = "hh_hunger_freq",
      `Go a whole day and night without eating anything at all because there was not enough food` = "fs_not_enough_food",
      `Livestock decrease Disease outbreak` = "reason_livestock_decrease/disease_outbreak",
      `Livestock decrease Flooding` = "reason_livestock_decrease/flooding_flooding",
      `Livestock decrease Drought` = "reason_livestock_decrease/drought_drought",
      `Recent displacement Flooding (riverine and flash flood)` = "factors_recent_displacement/flooding",
      `Recent displacement Drought (lack of food, water, livestock loss)` = "factors_recent_displacement/drought",
      `Recent displacement Desert locust invasion` = "factors_recent_displacement/desert_locust",
      `Have access to your current shelter in the next 6 months` = "shelter_access",
      `Latitude` = "Lat",
      `Longitude` = "Lon",
      `uuid` = "uuid"
    )
  }
  if(country_code=="nga"){
    res <- list(
      `State` = "state",
      `Population Group` = "pop_group",
      `Gender HoH` = "gender_hoh",
      `Age HoH` = "age_hoh",
      `Household size` = "hh_size",
      `Income estimate` = "overall_income_estimate",
      `Own livelihood assets` = "own_asset_hh",
      `Amount debt` = "amount_of_debt",
      `Own production` = "prim_source_of_food/own_prod",
      `Shock Drought` = "diff_or_shocks/drought",
      `Shock Flooding` = "diff_or_shocks/too_much_rain",
      `Own farm animal` = "hoh_own_farm_animal",
      `Land access` = "land_access_for_cultivation",
      `Food unavailable` = "food_of_anykind",
      `Food received` = "assistance_received_yn/food",
      `Main HH need` = "hh_first_priority_need",
      `Flooding Incident` = "nature_safety_incident/flooding",
      `Livestock decrease (rain)` = "hoh_livestock_decrease/drought",
      `Humanitarian assistance Flood` = "barriers_humanitarian_assistance/yes_poor",
      `Cash LSG` = "cash_lsg",
      `Lack income coping` = "cash_crit_ind",
      `Food LSG` = "food_lsg",
      `Not enough food` = "food_crit_ind1",
      `Shock regarding food` = "food_crit_ind2",
      `Health LSG` = "health_lsg",
      `Access health care` = "health_crit_ind1",
      `Challenges health care` = "health_crit_ind2",
      `WASH LSG` = "wash_lsg",
      `WASH water source` = "wash_crit_ind1",
      `WASH enough water` = "wash_crit_ind3",
      `Shelter LSG` = "shelter_lsg",
      `Shelter damage and enclosure issues` = "shelter_crit_ind",
      `Protection LSG` = "protection_lsg",
      `Education LSG` = "education_lsg",
      `MSNI` = "msni"
    )
    
  }
  
  # select the given columns on the fetched msna dataset
  df_msna_cols <- input_df |>
    select(any_of(purrr::map_chr(res, ~.x)), starts_with("rs_")) |>
    mutate(country_code = country_code)
  
  return(df_msna_cols)
}


```

