---
title: "aa-som_prelim_stat_msna_rs"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{aa-som_prelim_stat_msna_rs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE,
  collapse = TRUE,
  comment = "#>",
  warning = F, 
  message = F
)
```


```{r}
#library(GeoMSNA2022)
devtools::load_all()
library(here)
library(tidyverse)
library(openxlsx)
library(purrr)
library(srvyr)
library(illuminate)
library(sf)
library(jtools)
options(scipen = 999)

```

```{r}
df_msna_dataset <-  read_csv(file.path(
  Sys.getenv("MSNA2022_DIR"),"som","inputs","som_clean_msna_with_rs_hex.csv")
  )
```
# SOM MSNA and RS {.tabset}

## SOM MSNA RS Preliminary Analysis FCS, rCSI {.tabset}

### NDVI

#### Food Consumption Score (FCS) and NDVI

```{r}
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jun2022", "fcs")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jun2022", "fcs")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jun2022", "fcs")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jul2022", "fcs")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jul2022", "fcs")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jul2022", "fcs")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Aug2022", "fcs")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Aug2022", "fcs")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Aug2022", "fcs")

```

#### Reduced Coping Strategy Index (RCSI) and NDVI

```{r}
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jun2022", "rcsi")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jun2022", "rcsi")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jun2022", "rcsi")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jul2022", "rcsi")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jul2022", "rcsi")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jul2022", "rcsi")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Aug2022", "rcsi")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Aug2022", "rcsi")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Aug2022", "rcsi")
```

### VCI

#### Food Consumption Score (FCS) and VCI

```{r}
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jun2022", "fcs")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jul2022", "fcs")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Aug2022", "fcs")

```

#### Reduced Coping Strategy Index (RCSI) and VCI

```{r, echo=FALSE}
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jun2022", "rcsi")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jul2022", "rcsi")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Aug2022", "rcsi")

```

### SPI

#### Food Consumption Score (FCS) and SPI

```{r}
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi1", "fcs")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi3", "fcs")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi6", "fcs")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi9", "fcs")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi12", "fcs")

```

#### Reduced Coping Strategy Index (RCSI) and SPI

```{r}
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi1", "rcsi")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi3", "rcsi")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi6", "rcsi")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi9", "rcsi")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi12", "rcsi")

```

## Tools RS related indicators  {.tabset}

### NDVI

#### total_house_income and NDVI

```{r}
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jun2022", "total_house_income")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jun2022", "total_house_income")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jun2022", "total_house_income")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jul2022", "total_house_income")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jul2022", "total_house_income")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jul2022", "total_house_income")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Aug2022", "total_house_income")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Aug2022", "total_house_income")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Aug2022", "total_house_income")
```

#### total_hh_debt and NDVI

```{r}
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jun2022", "total_hh_debt")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jun2022", "total_hh_debt")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jun2022", "total_hh_debt")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jul2022", "total_hh_debt")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jul2022", "total_hh_debt")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jul2022", "total_hh_debt")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Aug2022", "total_hh_debt")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Aug2022", "total_hh_debt")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Aug2022", "total_hh_debt")
```

#### drinking_water and NDVI

```{r}
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jun2022", "drinking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jun2022", "drinking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jun2022", "drinking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jul2022", "drinking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jul2022", "drinking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jul2022", "drinking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Aug2022", "drinking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Aug2022", "drinking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Aug2022", "drinking_water")
```

#### cooking_water and NDVI

```{r}
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jun2022", "cooking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jun2022", "cooking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jun2022", "cooking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jul2022", "cooking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jul2022", "cooking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jul2022", "cooking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Aug2022", "cooking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Aug2022", "cooking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Aug2022", "cooking_water")
```

#### hh_fsl_shocks/drought and NDVI

```{r}
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jun2022", "hh_fsl_shocks/drought")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jun2022", "hh_fsl_shocks/drought")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jun2022", "hh_fsl_shocks/drought")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jul2022", "hh_fsl_shocks/drought")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jul2022", "hh_fsl_shocks/drought")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jul2022", "hh_fsl_shocks/drought")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Aug2022", "hh_fsl_shocks/drought")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Aug2022", "hh_fsl_shocks/drought")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Aug2022", "hh_fsl_shocks/drought")
```

#### hh_fsl_shocks/crop_disease and NDVI

```{r}
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jun2022", "hh_fsl_shocks/crop_disease")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jun2022", "hh_fsl_shocks/crop_disease")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jun2022", "hh_fsl_shocks/crop_disease")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jul2022", "hh_fsl_shocks/crop_disease")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jul2022", "hh_fsl_shocks/crop_disease")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jul2022", "hh_fsl_shocks/crop_disease")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Aug2022", "hh_fsl_shocks/crop_disease")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Aug2022", "hh_fsl_shocks/crop_disease")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Aug2022", "hh_fsl_shocks/crop_disease")
```

#### hh_fsl_shocks/flooding and NDVI

```{r}
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jun2022", "hh_fsl_shocks/flooding")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jun2022", "hh_fsl_shocks/flooding")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jun2022", "hh_fsl_shocks/flooding")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Jul2022", "hh_fsl_shocks/flooding")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Jul2022", "hh_fsl_shocks/flooding")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Jul2022", "hh_fsl_shocks/flooding")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_Aug2022", "hh_fsl_shocks/flooding")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_pct_median_Aug2022", "hh_fsl_shocks/flooding")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_NDVI_z_score_Aug2022", "hh_fsl_shocks/flooding")
```

### VCI

#### total_house_income and VCI

```{r}
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jun2022", "total_house_income")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jul2022", "total_house_income")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Aug2022", "total_house_income")
```

#### total_hh_debt and VCI

```{r}
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jun2022", "total_hh_debt")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jul2022", "total_hh_debt")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Aug2022", "total_hh_debt")
```

#### drinking_water and VCI

```{r}
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jun2022", "drinking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jul2022", "drinking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Aug2022", "drinking_water")
```

#### cooking_water and VCI

```{r}
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jun2022", "cooking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jul2022", "cooking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Aug2022", "cooking_water")
```

#### hh_fsl_shocks/drought and VCI

```{r}
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jun2022", "hh_fsl_shocks/drought")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jul2022", "hh_fsl_shocks/drought")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Aug2022", "hh_fsl_shocks/drought")
```

#### hh_fsl_shocks/crop_disease and VCI

```{r}
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jun2022", "hh_fsl_shocks/crop_disease")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jul2022", "hh_fsl_shocks/crop_disease")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Aug2022", "hh_fsl_shocks/crop_disease")
```

#### hh_fsl_shocks/flooding and VCI

```{r}
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jun2022", "hh_fsl_shocks/flooding")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Jul2022", "hh_fsl_shocks/flooding")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_VCI_Aug2022", "hh_fsl_shocks/flooding")
```

### SPI

#### total_house_income and SPI

```{r}
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi1", "total_house_income")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi3", "total_house_income")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi6", "total_house_income")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi9", "total_house_income")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi12", "total_house_income")
```

#### total_hh_debt and SPI

```{r}
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi1", "total_hh_debt")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi3", "total_hh_debt")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi6", "total_hh_debt")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi9", "total_hh_debt")
hex_plot_mean_rs_mean_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi12", "total_hh_debt")
```

#### drinking_water and SPI

```{r}
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi1", "drinking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi3", "drinking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi6", "drinking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi9", "drinking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi12", "drinking_water")
```

#### cooking_water and SPI

```{r}
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi1", "cooking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi3", "cooking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi6", "cooking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi9", "cooking_water")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi12", "cooking_water")
```

#### hh_fsl_shocks/drought and SPI

```{r}
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi1", "hh_fsl_shocks/drought")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi3", "hh_fsl_shocks/drought")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi6", "hh_fsl_shocks/drought")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi9", "hh_fsl_shocks/drought")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi12", "hh_fsl_shocks/drought")
```

#### hh_fsl_shocks/crop_disease and SPI

```{r}
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi1", "hh_fsl_shocks/crop_disease")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi3", "hh_fsl_shocks/crop_disease")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi6", "hh_fsl_shocks/crop_disease")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi9", "hh_fsl_shocks/crop_disease")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi12", "hh_fsl_shocks/crop_disease")
```

#### hh_fsl_shocks/flooding and SPI

```{r}
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi1", "hh_fsl_shocks/flooding")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi3", "hh_fsl_shocks/flooding")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi6", "hh_fsl_shocks/flooding")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi9", "hh_fsl_shocks/flooding")
hex_plot_mean_rs_count_msna_ind(df_msna_dataset, "GRID_ID", "rs_Jun_spi12", "hh_fsl_shocks/flooding")
```




<!-- # `Livestock decrease Disease outbreak` = "reason_livestock_decrease/disease_outbreak", -->
<!-- # `Livestock decrease Flooding` = "reason_livestock_decrease/flooding_flooding", -->
<!-- # `Livestock decrease Drought` = "reason_livestock_decrease/drought_drought", -->
