---
title: "ab-nga_prelim"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ab-nga_prelim}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(GeoMSNA2022)
library(tidyverse)
library(janitor)
library(xlsf)
library(sf)
library(leaflet)
devtools::load_all()


df <- load_hh_data(country_code = "nga")
kobo <- load_questionnaire(country_code = "nga") 
df <- xlsf::xlsf_relevel(df = df,xlsf = kobo,skip = "ward_of_origin")

```

## Income

NGA team indicates that income/poverty seems to be main driver of need. Let's dig deeper - examine tool:

```{r}
xlsf::xlsf_query(kobo,"income",.col="xml_name")
```


`overall_income_estimate` looks like the main indicator of interest on income: "Can you estimate your household's overall income, in local currency, over the course of the last 30 days? "

Here is a break down of those answers:
```{T}
df |> 
  ggplot(aes(x= overall_income_estimate))+
  geom_bar(stat="count")+
  coord_flip()+
  theme_bw()
```

So if this is driving needs/conditions... what is driving this?

Looking at raw %s there looks to be a difference in female vs male HoH with male HoH having considerably more income in last 30 days.

```{r}
df |> 
  group_by(gender_hoh,overall_income_estimate) |> 
  summarise(
    count=n()
  ) |> 
  mutate(pct= count/sum(count)) |> 
  
  ggplot(aes(x= overall_income_estimate,
             y=pct,
             fill = gender_hoh))+
  geom_bar(stat="identity",position= "dodge")+
  coord_flip()+
  theme_bw()
```


Land cover broken down by income group is interesting. We see that big spike in the "Sokoto millet, cowpeas, grondnuts, and livestock" landcover class in the highest income group.

```{r}
chart_pal_auto <- RColorBrewer::brewer.pal(n = 6,name = "Accent")
df <- df |> 
  mutate(
    overall_income_estimate=xlsf:::label_xml(xlsf = kobo_df,q_name = "overall_income_estimate")
  )
lulc_stats <- df |> 
  filter(!is.na(longitude)) |> 
  filter(!is.na(rs_nga.lznameend)) |> 
  group_by(overall_income_estimate,rs_nga.lznameend) |> 
  summarise(
    count=n()
  ) |> 
  mutate(pct= count/sum(count))

income_grp_n <- lulc_stats |> 
  summarise(stat= sum(count))

lulc_stats|> 
  mutate(pct= count/sum(count)) |> 
  # filter(overall_income_estimate=="more_than") |> pull(pct) |> sum()\
  ggplot(aes(x= overall_income_estimate,
             y=pct,
             fill = rs_nga.lznameend))+
  geom_bar(stat="identity",position= "dodge")+
  geom_text(data = income_grp_n, 
            aes(label=stat,x=overall_income_estimate,y=0.5, fill=NULL)) + 

  scale_y_continuous(labels = scales::percent)+
  scale_fill_manual(values=chart_pal_auto)+
  labs( x="HH Income Estimate (last 30 days)",y= "% HHs",
        title= "Estimate HH Income by Livelihood Zone",
        subtitle = "Northern Nigeria MSNA 2022 + Land Use",
        caption = "We see an increase in % HHs in the 'Sokoto millet, cowpeas, groundnuts, and livestock' livelihood class\nin the highest income group. Additionally we see 'flood plain rice and fishing' %s decrease as we lok at higher income groups"
        )+
  coord_flip()+
  theme_bw()+
  theme(
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    plot.caption = element_text(hjust = 0)
  )

# # breakdown other way?
# lulc_stats <- df |> 
#   filter(!is.na(longitude)) |> 
#   filter(!is.na(rs_nga.lznameend)) |> 
#   group_by(rs_nga.lznameend,overall_income_estimate) |> 
#   summarise(
#     count=n()
#   ) |> 
#   mutate(pct= count/sum(count))
# 
# income_grp_n <- lulc_stats |> 
#   summarise(stat= sum(count))
# 
# lulc_stats|> 
#   mutate(pct= count/sum(count)) |> 
#   # filter(overall_income_estimate=="more_than") |> pull(pct) |> sum()\
#   ggplot(aes(x= overall_income_estimate,
#              y=pct,
#              fill = rs_nga.lznameend))+
#   geom_bar(stat="identity",position= "dodge")+
#   geom_text(data = income_grp_n, 
#             aes(label=stat,x=overall_income_estimate,y=0.5, fill=NULL)) + 
# 
#   scale_y_continuous(labels = scales::percent)+
#   scale_fill_manual(values=chart_pal_auto)+
#   labs( x="HH Income Estimate (last 30 days)",y= "% HHs",
#         title= "Estimate HH Income by Land use/cover",
#         subtitle = "Northern Nigeria MSNA 2022 + Land Use",
#         caption = "We see an increase in % HHs in the 'Sokoto millet, cowpeas, groundnuts, and livestock' livelihood class\nin the highest income group. Additionally we see 'flood plain rice and fishing' %s decrease as we lok at higher income groups"
#         )+
#   coord_flip()+
#   theme_bw()+
#   theme(
#     legend.title = element_blank(),
#     axis.title.x = element_blank(),
#     plot.caption = element_text(hjust = 0)
#   )
# 



```

Let's see if we can understand anything more about this land cover pattern

```{r}

# https://fews.net/sites/default/files/documents/reports/NG_LZ_2018.pdf
landuse_chart_pal <- c(central_sorghum= "#1c561cff",
                       kano_sahelian ="#ffff9bff",
                       kano_sudanian="#f4c200ff",
                       nw_sorghum="#f3c275ff",
                       sokoto_rima_rice = "#5d5fd0ff",
                       sokoto_millet= "#ffff01ff"
                       )


RColorBrewer::display.brewer.all()

df |> 
  filter(gender_hoh=="male" & `hh_situation/catte_rearing`) |> 
  # count(gender_hoh)
  filter(!is.na(longitude)) |> 
  filter(!is.na(rs_nga.lznameend)) |> 
  group_by(overall_income_estimate,rs_nga.lznameend) |> 
  summarise(
    count=n()
  ) |> 
  mutate(pct= count/sum(count)) |> 
  # filter(overall_income_estimate=="more_than") |> pull(pct) |> sum()\
  ggplot(aes(x= overall_income_estimate,
             y=pct,
             fill = rs_nga.lznameend))+
  geom_bar(stat="identity",position= "dodge")+
  scale_fill_manual(values=chart_pal_auto)+
  scale_y_continuous(labels = scales::percent)+
  coord_flip()+
  theme_bw()


hh_income_generation <- df |> 
  select(starts_with("hh_situation/")) |> colnames()

non_cattle_gen <- setdiff(x=hh_income_generation ,y = "hh_situation/catte_rearing")


df |> 
  filter(!is.na(longitude)) |> 
  filter(!is.na(rs_nga.lznameend)) |> 
  group_by(overall_income_estimate,i.have_cattle=`hh_situation/catte_rearing`) |> 
  summarise(
    count=n()
  ) |> 
  mutate(pct= count/sum(count)) |> 
  # filter(overall_income_estimate=="more_than") |> pull(pct) |> sum()\
  ggplot(aes(x= overall_income_estimate,
             y=pct,
             fill = i.have_cattle))+
  geom_bar(stat="identity",position= "dodge")+
  coord_flip()+
  theme_bw()
```


Are people in livestock zones more likely to have livestock - should be?

Table below shows something 
```{r}
library(srvyr)
dfsvy_overall <-  as_survey(.data = df,weights= weight_both)

have_livestock_vs_lhz_tbl <- dfsvy_overall |> 
  filter(!is.na(longitude),!is.na(rs_nga.lznameend)) |> 
  group_by(rs_nga.lznameend,i.have_cattle=`hh_situation/catte_rearing`) |> 
  summarise(
    pct_weighted= survey_mean(vartype = "ci"),
    # pct_unweighted=mean(unweighted(i.have_cattle),na.rm=T),
    n = unweighted(n())
  ) |> 
  filter(i.have_cattle) |> 
  arrange(desc(pct_weighted))


have_livestock_vs_lhz_tbl |> 
  mutate(
    lhz= str_replace_all(rs_nga.lznameend,":","\n"),
    lhz= str_replace_all(lhz,",",",\n"),
    lhz= str_replace_all(lhz,"-Kano",",\n")
         
         ) |> 
  ggplot(aes(x= reorder(lhz,pct_weighted),
             y=pct_weighted
  ))+
  geom_bar(stat="identity",position= "dodge")+
  scale_y_continuous(labels = scales::percent)+
  labs(x="Livelihood Zone")+
  ggtitle("% HHs with livestock by livelihood zone",
          subtitle = "can MSNA data be used to inform LHZ data?")+
  coord_flip()+
  theme_bw()+
  theme(
    axis.title.x = element_blank()
  )

 
 DT::datatable(have_livestock_vs_lhz_tbl)
```


```{r}

dfsvy_overall |> 
  filter(!is.na(longitude),!is.na(rs_nga.lznameend)) |> 
  group_by(rs_nga.lznameend) |> 
  summarise(
    # pct_weighted= survey_mean(),
    n_weighted = survey_count(`hh_situation/catte_rearing`)
  ) |>
  # filter(i.have_cattle) |> 
  arrange(desc(pct_weighted))

# |> 
  mutate(pct= count/sum(count)) |> 
  filter(i.have_cattle) |> 
  arrange(desc(pct))
# so people in livestock zones do not look much more likely to have livestock do they?
df |> 
  filter(!is.na(longitude)) |> 
  filter(!is.na(rs_nga.lznameend)) |> 
  group_by(rs_nga.lznameend,i.have_cattle=`hh_situation/catte_rearing`) |> 
  summarise(
    count=n()
  ) |> 
  mutate(pct= count/sum(count)) |> 
  # filter(overall_income_estimate=="more_than") |> pull(pct) |> sum()\
  ggplot(aes(x= rs_nga.lznameend,
             y=pct,
             fill = i.have_cattle))+
  geom_bar(stat="identity",position= "dodge")+
  coord_flip()+
  theme_bw()



```

How about farmers and NDVI
```{r}

df$`hh_situation/farming` |> janitor::tabyl()

df  |> 
  filter(`hh_situation/farming`) |> 
  ggplot(aes(x=overall_income_estimate ,y=rs_ndvi_z_growing_season_21))+
  geom_violin()+
  labs(x="Income", 
       y= "NDVI Z over growing season",
       title = "Distance from HH to nearest detected water by whether HH reported flood/rain shock",
       subtitle = "Northern Nigeria - MSNA 2022 + JRC",
       caption ="Flood events more likely to be reported in communities closer to water" 
       ) +
  coord_flip()+
  theme_bw()+
  theme(
    plot.caption = element_text(hjust = 0)
  )
df  |> 
  filter(`hh_situation/farming`) |> 
  ggplot(aes(x=overall_income_estimate ,y=rs_rx10d_90d_may))+
  geom_violin()+
  labs(x="Income", 
       y= "NDVI Z over growing season",
       title = "Distance from HH to nearest detected water by whether HH reported flood/rain shock",
       subtitle = "Northern Nigeria - MSNA 2022 + JRC",
       caption ="Flood events more likely to be reported in communities closer to water" 
       ) +
  coord_flip()+
  theme_bw()+
  theme(
    plot.caption = element_text(hjust = 0)
  )

# got some functions below to find optimal crossings.... nothing too conclusive yet though
df  |> 
  # filter(`hh_situation/farming`) |> 
  ggplot(aes(x=overall_income_estimate ,y=rs_May_spi9 ))+
  geom_boxplot()+
  labs(x="Income", 
       y= "SPI12 May 2022",
       title = "Distance from HH to nearest detected water by whether HH reported flood/rain shock",
       subtitle = "Northern Nigeria - MSNA 2022 + JRC",
       caption ="Flood events more likely to be reported in communities closer to water" 
       ) +
  coord_flip()+
  theme_bw()+
  theme(
    plot.caption = element_text(hjust = 0)
  )


df_farmers <- df  |> 
  filter(`hh_situation/farming`) 


rs_numerics_analyze <- df_farmers |> 
  select(starts_with("rs_")) |> 
  select(where(is.numeric)) |> 
  select(-contains("fraction"),-contains("O2")) |> colnames()


df_farmers |> 
  group_by(overall_income_estimate) |> 
  summarise(
    across(.cols = all_of(rs_numerics_analyze),~median(scale(.x),na.rm=T))
  ) |> 
  summarise(
    across(.cols = all_of(rs_numerics_analyze),~sd(.x))
    ) |> pivot_longer(everything()) |> arrange(desc(value))
df |> 
  group_by(overall_income_estimate) |> 
  summarise(
    across(.cols = all_of(rs_numerics_analyze),~median(scale(.x),na.rm=T))
  ) |> 
  summarise(
    across(.cols = all_of(rs_numerics_analyze),~sd(.x))
    ) |> pivot_longer(everything()) |> arrange(desc(value))

rs_ndvi_z_growing_season_21
  
```


# Shocks
```{r}

xlsf_query(xlsf = kobo, pattern = "diff_or_shocks",.col = "xml_name")

df |> 
  count(`shock_impact_ability` )

df |> 
  ggplot(aes(x=`diff_or_shocks/drought` ,
             y=rs_ndvi_z_growing_season_21))+
  geom_boxplot()


df$`difficulty_type_hh/none` |> janitor::tabyl()
df |> 
  filter(shock_impact_ability%in% c("yes","no")) |> 
  group_by(overall_income_estimate, shock_impact_ability) |> 
  summarise(
    count=n()
  ) |> 
  mutate(
    pct= count/sum(count)
  ) |> 
  filter(shock_impact_ability=="yes") |> 
  ggplot(aes(x=overall_income_estimate,
             y= pct))+
  geom_bar(stat="identity",
           position= "dodge",
           fill ="#EE5858", color="black")+
  scale_y_continuous(labels = scales::percent)+
  labs(x="Estimated Income (last 30 days)",
       title = "HHs who reported shock: Did the impact of shocks cause hunger in your household?",
       subtitle = "Northern Nigeria MSNA 2022",
       caption = "Approximately 12 % of HHs reported a difficulties/shocks over the last 6 months, but HHs in higher income groups have increased resiliency\nand ability to absorb shocks and were less affected"
       )+
  coord_flip()+
  theme_bw()+
  theme(
      plot.caption = element_text(hjust = 0),
      axis.title.x = element_blank() 
  )
  



```


```{r}
df |> 
  mutate(
    i.cattle_only= hh_situation=="catte_rearing"
    ) |> 
  # filter(gender_hoh=="male" & `hh_situation/catte_rearing`) |> 
  # count(gender_hoh)
  filter(!is.na(longitude)) |> 
  filter(!is.na(rs_nga.lznameend)) |> 
  group_by(i.cattle_only,overall_income_estimate) |> 
  summarise(
    count=n()
  ) |> 
  mutate(pct= count/sum(count)) |> 
  # filter(overall_income_estimate=="more_than") |> pull(pct) |> sum()\
  ggplot(aes(x= overall_income_estimate,
             y=pct,
             fill = i.cattle_only))+
  geom_bar(stat="identity",position= "dodge")+
  coord_flip()+
  theme_bw()





xlsf_query(xlsf = kobo, "hh_situation",.col = "xml_name")
```


```{r}

sp_cols <- c("remote_interview","gender_hoh","overall_income_estimate","rs_healthcare_accessibility2019")
dfsp <- st_as_sf(x = df |> filter(!is.na(longitude)), coords = c('longitude','latitude'),crs= 4326) 

# library(surveyGEER)
# library(rgee)
# library(tidyrgee)
# ee_Initialize()
# 
# nearest_water <- extract_nearest_water_pixel_distance(y = dfsp |>
#                                        select(new_uid=uuid) ,                  
#                                      water_type = "permanent",
#                                      scale = 30, via="drive")
# 
df <- df |>
  left_join(
    nearest_water |>
      select(-name) |> 
      rename(avg_dist_perm_water_pix = value),
    by = c("uuid"="new_uid")
    ) #|>
  # write_rds(file.path(Sys.getenv("NGA_MSNA2022"),"20221129_msna_with_rs_nga.rds"))
# dir("C:\\Users\\zack.arno\\ACTED\\Colin WALDER - data")


dfsp_in_person <- dfsp |>
  filter(!remote_interview)


lowest_income <- dfsp_in_person |> 
  filter(overall_income_estimate=="less_than")

dfsp_in_person |>
  st_drop_geometry() |>
  count(overall_income_estimate)


pal_val<- RColorBrewer::brewer.pal(n = 7,name = "YlGn")
# pal <- colorFactor(pal_val, domain = lowest_income$overall_income_estimate)


leaflet() |> 
  addProviderTiles(provider = leaflet::providers$CartoDB.DarkMatter) |> 
  addCircles(data= lowest_income,
             label=~overall_income_estimate
             )


  
```

```{r}
library(tidymodels)
df_in_person <- df |> 
  filter(!remote_interview,!is.na(longitude))
# install.packages("tidymodels")
set.seed(4595)

df_in_person |> dplyr::select(starts_with("rs_")) |> colnames() |> dput()

rs_pred_vars <- c("rs_rx10d_30d_may", "rs_rx3d_30d_may", "rs_rx5d_30d_may", "rs_rx10d_60d_may", 
"rs_rx3d_60d_may", "rs_rx5d_60d_may", "rs_rx10d_90d_may", "rs_rx3d_90d_may", 
"rs_rx5d_90d_may", "rs_NDVI_Mar2022", "rs_NDVI_pct_median_Mar2022", 
"rs_NDVI_z_score_Mar2022", "rs_VCI_Mar2022", "rs_NDVI_Apr2022", 
"rs_NDVI_pct_median_Apr2022", "rs_NDVI_z_score_Apr2022", "rs_VCI_Apr2022", 
"rs_NDVI_May2022", "rs_NDVI_pct_median_May2022", "rs_NDVI_z_score_May2022", 
"rs_VCI_May2022", "rs_May_spi12", "rs_May_spi1", "rs_May_spi3", 
"rs_May_spi6", "rs_May_spi9", "rs_city_accessibility2015", "rs_healthcare_accessbility_walking_only2019", 
"rs_healthcare_accessibility2019", "rs_ndvi_z_growing_season_21", 
"rs_Npp_2020", "rs_Npp_2021", "rs_Npp_Z_2020", "rs_Npp_Z_2021", 
"rs_Npp_mean_2020", "rs_Npp_mean_2021", "rs_Npp_median_2020", 
"rs_Npp_median_2021", "rs_Npp_pct_median_2020", "rs_Npp_pct_median_2021", 
"rs_alos_landforms", "rs_srtm_landforms", "rs_nga.lzcode", "rs_nga.lznameend", 
"rs_nga.lzclass")


preds <-  c("longitude","latitude","gender_hoh",rs_pred_vars)
outcome_var <- c("overall_income_estimate")


df_mod<- df_in_person |> select(all_of(c(preds, outcome_var)))
data_split <- initial_split(df_mod, prop = 0.75)

nga_train <- training(data_split)
nga_test  <- testing(data_split)

set.seed(234)
val_set <- validation_split(nga_train, 
                            # strata = children, 
                            prop = 0.80)
lr_spec <-  logistic_reg()
  # logistic_reg(penalty = tune(), mixture = 1) |> 
  # multinom_reg(penalty = tune(), mixture = 1) |> 
  # set_engine("glmnet")

lr_recipe <- 
  recipe(overall_income_estimate~.,data= nga_train) |> 
  step_dummy(all_nominal_predictors()) |> 
  step_normalize(all_predictors()) 
  
lr_workflow <- 
  workflow() %>% 
  add_model(lr_mod) %>% 
  add_recipe(lr_recipe)

lr_fit <- fit(lr_spec,
    overall_income_estimate~.,
    data= df_mod) #|> 

lr_fit |> summary()
  tidy() |> 
  print(n=50)

# lr_reg_grid <- tibble(penalty = 10^seq(-4, -1, length.out = 30))

# lr_reg_grid %>% top_n(-5) # lowest penalty values
lr_res <- 
  lr_workflow %>% 
  tune_grid(val_set,
            grid = lr_reg_grid,
            control = control_grid(save_pred = TRUE),
            metrics = metric_set(roc_auc))

lr_res

lr_plot <- 
  lr_res %>% 
  collect_metrics() %>% 
  ggplot(aes(x = penalty, y = mean)) + 
  geom_point() + 
  geom_line() + 
  ylab("Area under the ROC Curve") +
  scale_x_log10(labels = scales::label_number())

lr_plot 


top_models <-
  lr_res %>% 
  show_best("roc_auc", n = 15) %>% 
  arrange(penalty) 




rf_xy_fit


m1 <- glm(overall_income_estimate~longitude+latitude +gender_hoh+rs_healthcare_accessbility_walking_only2019,
    data = df_in_person,family = binomial)
summary(m1)

#Data frame with hp in ascending order
Predicted_data <- data.frame(var2=seq(
  min(df$var2), max(df$var2),len=500))
 
# Fill predicted values using regression model
Predicted_data$var1 = predict(
  logistic_model, Predicted_data, type="response")
 
# Plot Predicted data and original data points
plot(var1 ~ var2, data=df)
lines(var1 ~ var2, Predicted_data, lwd=2, col="green")


# load library ggplot2
library(ggplot2)
 
 
# Plot Predicted data and original data points
ggplot(df_in_person, aes(x=rs_healthcare_accessbility_walking_only2019, y=overall_income_estimate)) +
  geom_point() +
      stat_smooth(method="glm", color="green", se=FALSE,
                method.args = list(family=binomial))

```


```{r}
df|> 
  ggplot(aes(x= reorder(overall_income_estimate,overall_income_estimate),fill=as_factor(`source_of_income/income_own`)))+
  geom_bar(stat="count",position="dodge")+coord_flip()
df|> 
  ggplot(aes(x= overall_income_estimate,fill=as_factor(`source_of_income/no_income`)))+
  geom_bar(stat="count",position="dodge")+coord_flip()
df|> 
  ggplot(aes(x= overall_income_estimate,fill=as_factor(`source_of_income/sal_work`)))+
  geom_bar(stat="count",position="dodge")+coord_flip()

df |> count(source_of_income ) |> arrange(desc(n)) |> print(n=52)


df |> 
  ggplot(aes(x= overall_income_estimate,y = rs_NDVI_z_score_Mar2022))+
  geom_boxplot()

```


```{r}
# figure out what these columns mean
xlsf::xlsf_query(kobo,"enough_water_needs",.col="xml_name")
```

"not_enough" seems like an important one to look at first.           

```{r}

df |> 
  count(`reaseon_for_displacement/drought`)
df |> 
  count(enough_water_needs) |> 
  arrange(desc(n))

df |> 
  dplyr::select(starts_with("enough_water_needs")) |> 
  glimpse()

```


```{r}



need_fct_conversion <- list(`Cash LSG` = "cash_lsg",
      `Lack income coping` = "cash_crit_ind",
      `Food LSG` = "food_lsg",
      `Not enough food` = "food_crit_ind1",
      `Shock regarding food` = "food_crit_ind2",
      `Health LSG` = "health_lsg",
      `Access health care` = "health_crit_ind1",
      `Challenges health care` = "health_crit_ind2",
      `WASH LSG` = "wash_lsg",
      `WASH water source` = "wash_crit_ind1",
      `WASH enough water` = "wash_crit_ind3",
      `Shelter LSG` = "shelter_lsg",
      `Shelter damage and enclosure issues` = "shelter_crit_ind",
      `Protection LSG` = "protection_lsg",
      `Education LSG` = "education_lsg",
      `MSNI` = "msni") |> names()


df_sel <- df_sel |> 
  mutate(
    across(.cols = all_of(need_fct_conversion), .fns = ~ as_factor(.x))
  )
```


boxplots could b interesting
```{r}
df_sel |> 
  count(MSNI)

rs_numeric_colnames <- df_sel |> 
  select(starts_with("rs_")& where(is.numeric)) |> 
  colnames()

msni_rs_boxplots <- rs_numeric_colnames |> 
  purrr::map(
    ~ df_sel |> 
      ggplot(aes(x= MSNI, y=!!sym(.x)))+
      geom_boxplot()
  ) |> 
  set_names(rs_numeric_colnames)
```


# Shocks

- Very few reported drought or flooding shocks.
- reported flooding and drought had essentially no effect on MSNI

```{r}
df |>
  filter(!is.na(rs_avg_dist_perm_water_pix)) |> 
  ggplot(aes(x= `diff_or_shocks/too_much_rain`,y=rs_avg_dist_perm_water_pix/1000))+
  geom_boxplot()+
  labs(x="reported flood/rain event", 
       y= "Distance to nearest water (km)",
       title = "Distance from HH to nearest detected water by whether HH reported flood/rain shock",
       subtitle = "Northern Nigeria - MSNA 2022 + JRC",
       caption ="Flood events more likely to be reported in communities closer to water" 
       ) +
  theme_bw()+
  theme(
    plot.caption = element_text(hjust = 0)
  )

# as expected, don't really see relationship with distance to water and income

df |>
  filter(!is.na(rs_avg_dist_perm_water_pix)) |> 
  ggplot(aes(x= overall_income_estimate,y=rs_avg_dist_perm_water_pix/1000))+
  geom_boxplot()+
  labs(x="reported flood/rain event", 
       y= "Distance to nearest water (km)",
       title = "Distance from HH to nearest detected water by income group",
       subtitle = "Northern Nigeria - MSNA 2022 + JRC",
       caption ="As expected no relationship apparent" 
       ) +
  coord_flip()+
  theme_bw()+
  theme(
    plot.caption = element_text(hjust = 0)
  )

binary_pal<- colorFactor(palette = c("green","red"),domain = dfsp$`diff_or_shocks/too_much_rain`)
leaflet() |> 
  addTiles() |> 
  addCircles(data= dfsp |> filter(`diff_or_shocks/too_much_rain`),
             label= dfsp$`diff_or_shocks/too_much_rain`,
             fillColor = ~binary_pal(`diff_or_shocks/too_much_rain`),
             color = ~binary_pal(`diff_or_shocks/too_much_rain`)
             )



df$`diff_or_shocks/drought` |> janitor::tabyl()
df$`diff_or_shocks/too_much_rain` |> janitor::tabyl()
# "diff_or_shocks/drought",
 # "diff_or_shocks/too_much_rain",
df_sel |>
  count(`Shock Flooding`)

df_sel |> 
      ggplot(aes(x= as.character(`Shock Flooding`), y=as.numeric(MSNI)))+
      geom_boxplot()

df_sel |> 
      ggplot(aes(x= as.character(`Shock Drought`), y=as.numeric(MSNI)))+
      geom_boxplot()

```

### Shocks Flooding

```{r}
shock_flooding <- rs_numeric_colnames |> 
  purrr::map(
    ~ df_sel |> 
      ggplot(aes(x= as.character(`Shock Flooding`), y=!!sym(.x)))+
      geom_boxplot()
  ) |> 
  set_names(rs_numeric_colnames)


shock_flooding$rs_rx3d_30d_may
shock_flooding$rs_rx3d_60d_may
shock_flooding$rs_rx3d_90d_may

shock_flooding$rs_rx5d_30d_may
shock_flooding$rs_rx5d_60d_may
shock_flooding$rs_rx5d_90d_may

shock_flooding$rs_rx10d_30d_may
shock_flooding$rs_rx10d_60d_may
shock_flooding$rs_rx10d_90d_may


```

```{r}
msni_rs_boxplots$rs_NDVI_pct_median_May2022
msni_rs_boxplots$rs_ndvi_z_growing_season_21

```


### Health Care indicators
Not much relation to the health care indicators
```{r}
df_sel |> 
      ggplot(aes(x= as.character(`Access health care`), y=rs_healthcare_accessibility2019))+
      geom_boxplot()

df |> 
  ggplot(aes(x= nearest_health_care, y=rs_healthcare_accessibility2019))+
  geom_boxplot()+
  coord_flip()

df |> 
  ggplot(aes(x= nearest_health_care, y=rs_healthcare_accessbility_walking_only2019))+
  geom_boxplot()+
  coord_flip()

df |> 
  ggplot(aes(x= nearest_health_care_adult, y=rs_healthcare_accessbility_walking_only2019))+
  geom_boxplot()+
  coord_flip()
```


```{r}


df_agri <- df |> 
  filter(prim_source_of_food=="own_prod") |> 
  load_core_hh_indicators("nga")


msni_rs_boxplots <- rs_numeric_colnames |> 
  purrr::map(
    ~ df_agri |> 
      ggplot(aes(x= as.character(MSNI), y=!!sym(.x)))+
      geom_boxplot()+coord_flip()
  ) |> 
  set_names(rs_numeric_colnames)

shock_flooding_agri_hhs <- rs_numeric_colnames |> 
  purrr::map(
    ~ df_agri |> 
      ggplot(aes(x= as.character(`Shock Flooding`), y=!!sym(.x)))+
      geom_boxplot()
  ) |> 
  set_names(rs_numeric_colnames)

msni_rs_boxplots$rs_May_spi1
msni_rs_boxplots$rs_May_spi3
msni_rs_boxplots$rs_May_spi6
msni_rs_boxplots$rs_May_spi9
msni_rs_boxplots$rs_May_spi12



shock_flooding_agri_hhs$rs_rx3d_30d_may
shock_flooding_agri_hhs$rs_rx3d_60d_may
shock_flooding_agri_hhs$rs_rx3d_90d_may

shock_flooding_agri_hhs$rs_rx5d_30d_may
shock_flooding_agri_hhs$rs_rx5d_60d_may
shock_flooding_agri_hhs$rs_rx5d_90d_may

shock_flooding_agri_hhs$rs_rx10d_30d_may
shock_flooding_agri_hhs$rs_rx10d_60d_may
shock_flooding_agri_hhs$rs_rx10d_90d_may


```

```{r}
res_test<- fast_collapse2(df = df_sel,x_vec = ck,disag=NULL,wt = "wt",sm_sep = "/")
res_test |> View()
res_test |> 
  select(variable, variable_val, n_weighted, n_unweighted, `mean/pct`) |> View()
```


Access Health Care


```{r}


```
  8*5.1
```

