---
title: "ab-nga_prelim"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ab-nga_prelim}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(GeoMSNA2022)
library(tidyverse)
library(janitor)
library(xlsf)
devtools::load_all()
qs <-  readxl::read_excel(file.path(Sys.getenv("NGA_MSNA2022"),"nga_msna_2022_survey_choices.xlsx" ),sheet = "survey")
choices <-  readxl::read_excel(file.path(Sys.getenv("NGA_MSNA2022"),"nga_msna_2022_survey_choices.xlsx" ),sheet = "choices")


kobo<- xlsf::xlsf_load(survey = qs,choices = choices,label = "label::English",sm_sep ="/" )

df <- load_hh_data(country_code = "nga")



df_sel <- df |>
  load_core_hh_indicators("nga") 

df_sel |> 
  glimpse()

df$income

```

## Income

Recieved info from team that income/poverty seems to be main driver of need. Let's dig deepr into that first
```{r}

xlsf::xlsf_query(kobo,"income",.col="xml_name")
df <- xlsf::xlsf_relevel(df = df,xlsf = kobo,skip = "ward_of_origin")


```

```{T}
df |> 
  ggplot(aes(x= overall_income_estimate))+
  geom_bar(stat="count")+
  coord_flip()

df|> 
  ggplot(aes(x= reorder(overall_income_estimate,overall_income_estimate),fill=as_factor(`source_of_income/income_own`)))+
  geom_bar(stat="count",position="dodge")+coord_flip()
df|> 
  ggplot(aes(x= overall_income_estimate,fill=as_factor(`source_of_income/no_income`)))+
  geom_bar(stat="count",position="dodge")+coord_flip()
df|> 
  ggplot(aes(x= overall_income_estimate,fill=as_factor(`source_of_income/sal_work`)))+
  geom_bar(stat="count",position="dodge")+coord_flip()

df |> count(source_of_income ) |> arrange(desc(n)) |> print(n=52)


df |> 
  ggplot(aes(x= overall_income_estimate,y = rs_NDVI_z_score_Mar2022))+
  geom_boxplot()

```


```{r}
# figure out what these columns mean
xlsf::xlsf_query(kobo,"enough_water_needs",.col="xml_name")
```

"not_enough" seems like an important one to look at first.           

```{r}

df |> 
  count(`reaseon_for_displacement/drought`)
df |> 
  count(enough_water_needs) |> 
  arrange(desc(n))

df |> 
  dplyr::select(starts_with("enough_water_needs")) |> 
  glimpse()

```


```{r}



need_fct_conversion <- list(`Cash LSG` = "cash_lsg",
      `Lack income coping` = "cash_crit_ind",
      `Food LSG` = "food_lsg",
      `Not enough food` = "food_crit_ind1",
      `Shock regarding food` = "food_crit_ind2",
      `Health LSG` = "health_lsg",
      `Access health care` = "health_crit_ind1",
      `Challenges health care` = "health_crit_ind2",
      `WASH LSG` = "wash_lsg",
      `WASH water source` = "wash_crit_ind1",
      `WASH enough water` = "wash_crit_ind3",
      `Shelter LSG` = "shelter_lsg",
      `Shelter damage and enclosure issues` = "shelter_crit_ind",
      `Protection LSG` = "protection_lsg",
      `Education LSG` = "education_lsg",
      `MSNI` = "msni") |> names()


df_sel <- df_sel |> 
  mutate(
    across(.cols = all_of(need_fct_conversion), .fns = ~ as_factor(.x))
  )
```


boxplots could b interesting
```{r}
df_sel |> 
  count(MSNI)

rs_numeric_colnames <- df_sel |> 
  select(starts_with("rs_")& where(is.numeric)) |> 
  colnames()

msni_rs_boxplots <- rs_numeric_colnames |> 
  purrr::map(
    ~ df_sel |> 
      ggplot(aes(x= MSNI, y=!!sym(.x)))+
      geom_boxplot()
  ) |> 
  set_names(rs_numeric_colnames)
```


# Shocks

- Very few reported drought or flooding shocks.
- reported flooding and drought had essentially no effect on MSNI

```{r}

df_sel |>
  count(`Shock Flooding`)
df_sel |>
  count(`Shock Drought`)

df_sel |> 
      ggplot(aes(x= as.character(`Shock Flooding`), y=as.numeric(MSNI)))+
      geom_boxplot()

df_sel |> 
      ggplot(aes(x= as.character(`Shock Drought`), y=as.numeric(MSNI)))+
      geom_boxplot()

```

### Shocks Flooding

```{r}
shock_flooding <- rs_numeric_colnames |> 
  purrr::map(
    ~ df_sel |> 
      ggplot(aes(x= as.character(`Shock Flooding`), y=!!sym(.x)))+
      geom_boxplot()
  ) |> 
  set_names(rs_numeric_colnames)


shock_flooding$rs_rx3d_30d_may
shock_flooding$rs_rx3d_60d_may
shock_flooding$rs_rx3d_90d_may

shock_flooding$rs_rx5d_30d_may
shock_flooding$rs_rx5d_60d_may
shock_flooding$rs_rx5d_90d_may

shock_flooding$rs_rx10d_30d_may
shock_flooding$rs_rx10d_60d_may
shock_flooding$rs_rx10d_90d_may


```

```{r}
msni_rs_boxplots$rs_NDVI_pct_median_May2022
msni_rs_boxplots$rs_ndvi_z_growing_season_21

```


### Health Care indicators
Not much relation to the health care indicators
```{r}
df_sel |> 
      ggplot(aes(x= as.character(`Access health care`), y=rs_healthcare_accessibility2019))+
      geom_boxplot()

df |> 
  ggplot(aes(x= nearest_health_care, y=rs_healthcare_accessibility2019))+
  geom_boxplot()+
  coord_flip()

df |> 
  ggplot(aes(x= nearest_health_care, y=rs_healthcare_accessbility_walking_only2019))+
  geom_boxplot()+
  coord_flip()

df |> 
  ggplot(aes(x= nearest_health_care_adult, y=rs_healthcare_accessbility_walking_only2019))+
  geom_boxplot()+
  coord_flip()
```


```{r}


df_agri <- df |> 
  filter(prim_source_of_food=="own_prod") |> 
  load_core_hh_indicators("nga")


msni_rs_boxplots <- rs_numeric_colnames |> 
  purrr::map(
    ~ df_agri |> 
      ggplot(aes(x= as.character(MSNI), y=!!sym(.x)))+
      geom_boxplot()+coord_flip()
  ) |> 
  set_names(rs_numeric_colnames)

shock_flooding_agri_hhs <- rs_numeric_colnames |> 
  purrr::map(
    ~ df_agri |> 
      ggplot(aes(x= as.character(`Shock Flooding`), y=!!sym(.x)))+
      geom_boxplot()
  ) |> 
  set_names(rs_numeric_colnames)

msni_rs_boxplots$rs_May_spi1
msni_rs_boxplots$rs_May_spi3
msni_rs_boxplots$rs_May_spi6
msni_rs_boxplots$rs_May_spi9
msni_rs_boxplots$rs_May_spi12



shock_flooding_agri_hhs$rs_rx3d_30d_may
shock_flooding_agri_hhs$rs_rx3d_60d_may
shock_flooding_agri_hhs$rs_rx3d_90d_may

shock_flooding_agri_hhs$rs_rx5d_30d_may
shock_flooding_agri_hhs$rs_rx5d_60d_may
shock_flooding_agri_hhs$rs_rx5d_90d_may

shock_flooding_agri_hhs$rs_rx10d_30d_may
shock_flooding_agri_hhs$rs_rx10d_60d_may
shock_flooding_agri_hhs$rs_rx10d_90d_may


```

```{r}
res_test<- fast_collapse2(df = df_sel,x_vec = ck,disag=NULL,wt = "wt",sm_sep = "/")
res_test |> View()
res_test |> 
  select(variable, variable_val, n_weighted, n_unweighted, `mean/pct`) |> View()
```


Access Health Care


```{r}


```
  8*5.1
```

