---
title: "ad-col_prelim"
output: rmarkdown::html_vignette
author: Jhon Montero & Zack Arno
vignette: >
  %\VignetteIndexEntry{ad-col_prelim}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Libraries and any parameterization
```{r setup}
library(GeoMSNA2022)
library(readxl)
library(sf)
library(tidyverse)
library(srvyr)

devtools::load_all()
country_code="col"

# you can add more vars here 
vars_1_5_factor <-  c("msni")

#' fct_expand_relevel
#' @description for some reason fct_expand does not also relevel according to argument input order
#' therefore have made a wrapper to expand and then relevel
#' @param x  variable
#' @param levels factor levels to expand to and relevel according to input order
#'
#' @return vector releveled
fct_expand_relevel <-  function(x,levels){
  x_fct <- as_factor(x)
  x_expanded <-forcats::fct_expand(x_fct, levels)
  x_releveled <-  forcats::fct_relevel(x_expanded,levels)
  return(x_releveled)
}


```

## Load data and survey
```{r}
data <- read_excel(file.path(input_dir(country_code="col"),"REACH_COL_LSGMSNI_08112022.xlsx"),
                   guess_max = min(60000, n_max = NULL), sheet = "Sheet1")

ks <- read_excel(file.path(input_dir(country_code="col"),"MSNA-6ta ronda- Formulario final_v7.xlsx"), 
                     sheet = "survey",
                     guess_max = min(60000, n_max = NULL))

kc <- read_excel(file.path(input_dir(country_code="col"),
                                "MSNA-6ta ronda- Formulario final_v7.xlsx"),
                      sheet = "choices",
                      guess_max = min(60000, n_max = NULL))

gee <- readRDS(file.path(input_dir(country_code="col"),
                         "20221026_col_rs_indicators_with_uuid.rds"))

data_w_rs <- data |> 
  left_join(gee, by = c("uuid"))
```


some tools I've made that I find handy for working with kobo data `{xlsf}`
```{r}
qdf <- xlsf::xlsf_load(survey = survey,choices = choices, data_main = data_w_rs,sm_sep = "/")

# this just refactors dat according to kobo tool - it's nice pre processing step before aggregating
# so levels don't get dropped
qdf$data_main <- xlsf::xlsf_relevel(qdf$data_main,xlsf = qdf)

qdf$data_main <- qdf$data_main |> 
  mutate(
    across(
      .cols = all_of(vars_1_5_factor),
      .fns = ~fct_expand_relevel(x=.x,levels = c("1","2","3","4","5"))
  )
  )

```

create survey object for weighted calcs
```{r}
dfsvy <-  srvyr::as_survey(qdf$data_main, weight=pesos)
```

## Analysis

### Oxford access indicators

Travel time to the nearest hospital or clinic was extracted from the Oxford 2019  Malaria Atlas Project data set for each HH. It would be interesting to understand the relationship between this variable and various humanitarian conditions. 

Below we visualize average travel time by aggregated MSNI score. There appears to a relationship where increasing travel time correlates with higher MSNI scores. Some follow up points/thoughts: 

- Oxford access indicator may be a proxy/reflection of an urban-rural divide.
  + rural hhs living under harder conditions?
  + are there other layers with urban-rural delineations?

```{r}

dfsvy |> 
  group_by(msni) |> 
  summarise(
    distance_mean = survey_mean(rs_healthcare_accessibility2019,na.rm=T,"ci")
    ) |>
  left_join(
    #get raw counts
    dfsvy$variables |> 
  group_by(msni) |> 
  count()
  ) |> 
  ggplot(aes(x=msni,y=distance_mean,group=1))+
  geom_line(color = "red")+
  geom_errorbar(
    aes(ymin= `distance_mean_low`,
        ymax= `distance_mean_upp`), 
                width=0.2)+
  labs(x= "MSNI",y="Average Travel Time to Hospital/Clinic (minutes)")+
  geom_point()+
  geom_text(
            aes(label=n,x=msni,y=30, fill=NULL)) + 
  theme_bw()
```