---
title: "Remote Sensing & Survey Analytics"
subtitle: "Multi-Country Review"
author: "Zack Arno"
date: '2023-01-03'
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: FALSE
    theme:
      bg: "#D1D3D4"
      fg: "#58585A"
      primary: "#EE5859"
      base_font:
        google: "Roboto"
      code_font:
        google: "JetBrains Mono"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
thematic::thematic_on()
library(tidyverse)
library(srvyr)
library(here)
list.files("R",full.names = T) |> purrr::map(~source(.x))
targets::tar_load(nga_svy)
# tar_render(report_trigger_overview,"pipeline/drc_cholera_trigger_overview_report.Rmd"),
```

## Intro

In 2022 alongside typical MSNA analysis an exercise was done to investigate integrating remote sensing into the more classical survey analyses. A series of relevant RS indicators were chosen and the adapted for 6 specific contexts where MSNAs were being carried out. These six contexts were Niger, Somalia, Mali, Haiti,Colombia, Niger, Iraq. Using Google Earth Engine (GEE) the remote sensing indicators chosen were pulled directly into the household level data sets and provided back to the field teams for expert contextualization and alignment to countries analytic framework.

Along with the initial effort of extracting and sharing the RS data and the independent work of the country teams, this document and repository holds additional collaborative analyses for Somalia, Colombia, and Nigeria, Iraq. The countries selected for this document were chosen based on feedback and support received from the field.


## Overview

Below we show an overview map of the assessment activities carried out in Somalia, Nigeria,Iraq, and Colombia.
Not going to give an overview of each countries climate yet

```{r overviewmap}
summary(cars)
```


## Nigeria

### Income

Pretty clear in NGA that gender_hoh is a big driver of income with male headed households dominating the higher income brackets and female the lower income brackets. Therefore environmental analysis of hh_income should take this into account.

```{r}
nga_svy$data_main <- nga_svy$data_main |> 
  mutate(
        overall_income_estimate=xlsf:::label_vec_from_xml(xlsf = nga_svy,q_name = "overall_income_estimate"),
        nearest_health_care = xlsf:::label_vec_from_xml(xlsf=nga_svy, q_name="nearest_health_care")
  ) 


nga_svy$data_main  |> 
   group_by(gender_hoh,overall_income_estimate) |> 
  summarise(
    survey_mean(vartype = "ci")
  ) |> 
  ggplot(aes(x= overall_income_estimate, y=coef,color=gender_hoh))+
  geom_errorbar(aes(ymin=`_low`, ymax=`_upp`))+
  geom_point()+
  coord_flip()+ 
  theme_bw()
```




```{r}
nga_svy$data_main |> 
  group_by(overall_income_estimate,gender_hoh,i.have_cattle=`hh_situation/catte_rearing`) |> 
  summarise(
    pct_mean = survey_mean()
  ) |> 
  # filter(i.have_cattle==T) |>
  ggplot(aes(x= overall_income_estimate,
             y=pct_mean
             ))+
  geom_line(aes(group=overall_income_estimate) )+
  geom_point(aes(color=gender_hoh),stat="identity",position= "dodge")+
  facet_wrap(~i.have_cattle,scales = "free")+
  coord_flip()+
  theme_bw()
```


Does having cattle affect reported income bracket?

For female headed households it looks like the answer is no. For male headed households we see that the higher income brackets tend to be more likely to own cattle, whereas the lower income brackets do not.

```{r}
nga_svy$data_main |> 
  # filter(gender_hoh=="male") |> 
  group_by(gender_hoh,i.have_cattle=`hh_situation/catte_rearing`,overall_income_estimate) |> 
  summarise(
    pct_mean = survey_mean()
  ) |> 
  # filter(i.have_cattle==T) |>
  ggplot(aes(x= overall_income_estimate,
             y=pct_mean
             ))+
  geom_line(aes(group=overall_income_estimate) )+
  geom_point(aes(color=i.have_cattle),stat="identity",position= "dodge")+
  scale_y_continuous(labels = scales::percent)+
  facet_wrap(~gender_hoh,scales = "free")+
  coord_flip()+
  theme_bw()
```

```{r}
nga_svy$data_main |> 
  # filter(gender_hoh=="male") |> 
  group_by(gender_hoh,rs_alos_landforms,overall_income_estimate) |> 
  summarise(
    pct_mean = survey_mean()
  ) |> 
  # filter(i.have_cattle==T) |>
  ggplot(aes(x= overall_income_estimate,
             y=pct_mean
             ))+
  # geom_line(aes(group=overall_income_estimate) )+
  # geom_point(aes(color=i.have_cattle),stat="identity",position= "dodge")+
  geom_bar(aes(fill=rs_alos_landforms),stat="identity",position= "dodge")+
  scale_y_continuous(labels = scales::percent)+
  facet_wrap(~gender_hoh,scales = "free")+
  coord_flip()+
  theme_bw()

nga_svy$data_main |> 
  # filter(gender_hoh=="male") |> 
  group_by(gender_hoh,overall_income_estimate,rs_alos_landforms) |> 
  summarise(
    pct_mean = survey_mean()
  ) |> 
  # filter(i.have_cattle==T) |>
  ggplot(aes(x= overall_income_estimate,
             y=pct_mean
             ))+
  # geom_line(aes(group=overall_income_estimate) )+
  # geom_point(aes(color=i.have_cattle),stat="identity",position= "dodge")+
  geom_bar(aes(fill=rs_alos_landforms),stat="identity",position= "dodge")+
  scale_y_continuous(labels = scales::percent)+
  facet_wrap(~gender_hoh,scales = "free")+
  coord_flip()+
  theme_bw()

```

### Accessibility

Oxford Malaria project produced a global RS dataset in 2019 that predicts walking and total travel times to nearest health center. Here we test it against HH reports of travel times to nearest health center.

```{r}

nga_svy$data_main |> 
  group_by(nearest_health_care) |> 
  summarise(
    pct_mean = survey_mean(rs_healthcare_accessbility_walking_only2019,na.rm=T,vartype="ci"),
    n_unweighted=unweighted(n())
  ) |> 
  ggplot(aes(x= nearest_health_care,
             y=pct_mean
             ))+
  geom_point()+
  geom_errorbar(aes(ymin=pct_mean_low, ymax= pct_mean_upp, width=0.2))+
  geom_line(group=1)+
  geom_text(aes(label=n_unweighted,x=nearest_health_care,y=23, fill=NULL)) +
  scale_y_continuous()+
  labs(x="Reported Travel Time",
       y="Remotely sensed walking time to healthcare facility (minutes)",
         title = "Do reported walking travel times to nearest healthcare facility correlate with remotely sensed travel time?",
       subtitle = "Northern Nigeria MSNA 2022",
       caption = str_wrap("We see that the remotely sensed walking times to nearest health center do generally correlate with  HH reported travel times. However, RS calculations for HHs that reported over 15 minutes travel time do appear to be too low",180)
  )+
  theme_bw()+
  theme(
    plot.caption = element_text(hjust = 0),
  )
```


Does the distance corroborate with accessibility indicators? yes it does, but results are under estimated

```{r}
nga_svy$data_main |> 
  mutate(
    i.nearest_healthcare_barrier = case_when(
      nearest_health_care_adult %in% c("no_barriers","did_not_need")~"No Barrier",
      nearest_health_care_adult == "no_facility_nearby"~"Too Far",
      TRUE~NA_character_
      )
  ) |> 
  filter(!is.na(i.nearest_healthcare_barrier)) |> 
  group_by(i.nearest_healthcare_barrier) |> 
  summarise(
    pct_mean = survey_mean(rs_healthcare_accessbility_walking_only2019,na.rm=T,vartype="ci"),
    n_unweighted=unweighted(n())
  ) |> 
  ggplot(aes(x= i.nearest_healthcare_barrier,
             y=pct_mean
             ))+
  geom_point()+
  geom_errorbar(aes(ymin=pct_mean_low, ymax= pct_mean_upp, width=0.2))+
  # geom_line(group=1)+
  geom_text(aes(label=n_unweighted,x=i.nearest_healthcare_barrier,y=23, fill=NULL)) +
  scale_y_continuous()+
    labs(x="Barrier to accessing facility?",
       y="Remotely sensed walking time to healthcare facility (minutes)",
         title = "RS does indicate farther walking times for those reporting distance as a barrier to accessing healthcare",
       subtitle = "Northern Nigeria MSNA 2022",
       caption = str_wrap("RS does corraborate, but the distances do appear underestimated",180)
  )+
  theme_bw()+
  theme(
    plot.caption = element_text(hjust = 0),
  )
```


### MSNI

It looks like increased rainfall intensify associated with increased MSNI needs, but there is weird spatial element.

```{r}

nga_svy$data_main |> 
   group_by(msni=as_factor(msni)) |> 
  summarise(
    mean_pct = survey_mean(rs_rx5d_90d_may,na.rm=T,vartype = "ci")
  ) |> 
    ggplot(aes(x= msni,
             y=mean_pct
  ))+
  geom_point(stat="identity")+
  geom_line(group=1)+
    geom_errorbar(
    aes(ymin = `mean_pct_low`,
        ymax = `mean_pct_upp`), 
                width = 0.2)+
  # geom_text(aes(label=n,x=variable_val ,y=20, fill=NULL)) +
  ggtitle(label = "NGA MSNA 2022: average max 5 day rainfall intensity by MSNI",
         subtitle = "Higher rainfall intensity is associated with higher MSNI needs")+
  labs(x="MSNI",
       y= "Average max 5 day rainfall intensity for May (mm)")+
  theme_bw()
```



### Shocks
 
```{r}
nga_svy$data_main |> 
  filter(shock_impact_ability%in% c("yes","no")) |> 
  group_by(overall_income_estimate,shock_impact_ability) |> 
  summarise(
    pct_weighted= survey_mean( vartype = "ci",na.rm=T),
    n = unweighted(n())
  ) |> 
  filter(shock_impact_ability=="yes") |> 
  ggplot(aes(x=overall_income_estimate,
             y= pct_weighted))+
  geom_point(color="black")+
  geom_errorbar(
    aes(ymin = `pct_weighted_low`,
        ymax = `pct_weighted_upp`), 
                width = 0.2)+
  
  scale_y_continuous(
    labels = scales::percent
    )+
  labs(x="Estimated Income (last 30 days)",
       title = "HHs who reported shock: Did the impact of shocks cause hunger in your household?",
       subtitle = "Northern Nigeria MSNA 2022",
       caption = "Approximately 12 % of HHs reported a difficulties/shocks over the last 6 months, but HHs in higher income groups have increased resiliency\nand ability to absorb shocks and were less affected"
       )+
  coord_flip()+
  theme_bw()+
  theme(
      plot.caption = element_text(hjust = 0),
      axis.title.x = element_blank() 
  )
```

generally true for both male and female hoh
```{r}
nga_svy$data_main |> 
  filter(shock_impact_ability%in% c("yes","no")) |> 
  group_by(overall_income_estimate,gender_hoh,shock_impact_ability) |> 
  summarise(
    pct_weighted= survey_mean( vartype = "ci",na.rm=T),
    n = unweighted(n())
  ) |> 
  filter(shock_impact_ability=="yes") |> 
  ggplot(aes(x=overall_income_estimate,
             y= pct_weighted))+
  geom_point(aes(color=gender_hoh))+
  geom_line(aes(color=gender_hoh, group=gender_hoh))+
  scale_y_continuous(
    labels = scales::percent
    )+
  labs(x="Estimated Income (last 30 days)",
       title = "HHs who reported shock: Did the impact of shocks cause hunger in your household?",
       subtitle = "Northern Nigeria MSNA 2022",
       caption = "Approximately 12 % of HHs reported a difficulties/shocks over the last 6 months, but HHs in higher income groups have increased resiliency\nand ability to absorb shocks and were less affected"
       )+
  coord_flip()+
  theme_bw()+
  theme(
      plot.caption = element_text(hjust = 0),
      axis.title.x = element_blank() 
  )

```

## Colombia



## Methodology

RS indicators were made an extracted using GEE. This work is contained in the `{surveyGEER}` repository. Generally the indicators were extracted at the pixel level. Temporal RS data sources with longer timelines were typically preferred over those with shorter time lines so that pixel-values could be normalized to standard scores and indices such as percent mean/median could be constructed.

